Gender and international diversity improves equity in peer review

### 2018-08-25 eLife_Analysis_and_Figures.Rmd
Update, push to submit

---
title: 'Gender and international diversity improves equity in peer review: R Notebook, August 2018'
author: "Dakota Murray"
output:
  html_document:
    df_print: paged
  html_notebook: default
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
  pdf_document: default
---

@@

> Figure 2. Left: Yearly count of initial submissions, encouraged initial submissions, and accepted full submissions to eLife between 2012 and 2016; Right: encourage rate of initial submissions, overall accept rate of initial submissions, and accept rate of full submissions between 2012 and 2016. Submissions during the year of 2017 were not included because we do not have sufficient data for full lifecycle of these manuscripts.

@@

p1 <- d1 %>%
  ggplot(aes(x = submission_year, y = measurement, linetype = measure_key, color = measure_key, shape = measure_key)) +
  geom_line() +
  geom_point(size = 2) +
  theme_dakota() +
  labs(
    x = "Submission Year",
    y = "Count of Manuscripts"
  ) +
  scale_color_manual(labels = c("accept_count" = "#Accepted", "encourage_count" = "#Encouraged", "paper_count" = "#Submitted"), values = c("black", "blue", "red")) +
  scale_shape_discrete(labels = c("accept_count" = "#Accepted", "encourage_count" = "#Encouraged", "paper_count" = "#Submitted")) +
  scale_linetype_discrete(labels = c("accept_count" = "#Accepted", "encourage_count" = "#Encouraged", "paper_count" = "#Submitted"))

d2 <- elife %>%
  group_by(submission_year) %>%
  summarize(
        paper_count = n(),
        accept_count = sum(accepted == TRUE, na.rm = T),
        encourage_count = sum(encouraged == TRUE, na.rm = T),
        encourage_rate = encourage_count / paper_count,
        accept_rate = accept_count / paper_count,
        encourage_accept_rate = accept_count / sum(!is.na(full_decision_made) & full_decision_made)
  ) %>%
  gather(measure_key, value = measurement, encourage_rate, accept_rate, encourage_accept_rate) %>%
  mutate(
    measure_key = factor(measure_key, levels = c("encourage_rate", "accept_rate", "encourage_accept_rate"))
  ) %>%
  filter(submission_year < 2017)

p2 <- d2 %>%
  ggplot(aes(x = submission_year, y = measurement, linetype = measure_key, color = measure_key, shape = measure_key)) +
  geom_line() +
  geom_point(size = 2) +
  ylim(0, 1) +
  theme_dakota() +
  labs(
    x = "Submission Year",
    y = "Rate"
  ) +
  scale_color_manual(labels = c("accept_rate" = "Overall Accept %", "encourage_rate" = "Encourage %", "encourage_accept_rate" = "Accept %"), 
                     values = c("blue", "red", "purple")) +
  scale_shape_manual(labels = c("accept_rate" = "Overall Accept %", "encourage_rate" = "Encourage %", "encourage_accept_rate" = "Accept %"),
                     values = c(17, 15, 18)) +
  scale_linetype_manual(labels = c("accept_rate" = "Overall Accept %", "encourage_rate" = "Encourage %", "encourage_accept_rate" = "Accept %"), 
                          values = c("dotted", "dashed", "dotdash"))

fig2 <- grid.arrange(p1, p2, ncol = 2)
ggsave("figures/main/fig_2.tiff", plot = fig2, height = 4, width = 7)
ggsave("figures/main/fig_2.png", plot = fig2, height = 4, width = 7)

@@

p1 <- people %>%
  filter(gender %in% c("M", "F")) %>%
  mutate(gender = ifelse(gender == "M", "Male", "Female")) %>%
  group_by(type) %>%
  mutate(total = n()) %>%
  group_by(type, gender) %>%
  summarize(
    prop = n() / total[1]
  ) %>%
  ungroup() %>%
  left_join(expected, by = "gender") %>%
  left_join(sig_df, by = c("gender", "type")) %>%
  mutate(
    type = factor(type, levels = c("Gatekeeper", "Corr. Author", "First Author", "Last Author"))
  ) %>%
  # start ggplot
  ggplot(aes(x = gender, y = prop, fill = gender)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_bar(stat = "identity", aes(y = expected_prop), alpha = 0, color = "black", fill = "white", size = 0.5, linetype = "dashed") +
  #geom_text(aes(label = paste0(round(prop, 3) * 100, "%"), y = 0.1), size = 3) +
  geom_text(aes(label = sig, x = 1.5, y = 0.9)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~type, nrow = 1) +
  theme_dakota() +
  ylim(c(0, 1)) +
  theme(
    axis.title.x = element_blank(),
    legend.position = "right"
  ) +
  labs(y = "Proportion") +
  guides(fill = F)

@@

p2 <- people %>%
  group_by(type) %>%
  mutate(total = n()) %>%
  filter(continent != "Antarctica") %>%
  group_by(type, continent) %>%
  summarize(
    prop = n() / total[1]
  ) %>%
  ungroup() %>%
  left_join(expected, by = "continent") %>%
  left_join(sig_df, by = c("continent", "type")) %>%
  mutate(
    type = factor(type, levels = c("Gatekeeper", "Corr. Author", "First Author", "Last Author")),
    continent = reorder(continent, -prop)
  ) %>%
  # start ggplot
  ggplot(aes(x = continent, y = prop, fill = continent)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_bar(stat = "identity", aes(y = expected_prop), alpha = 0, color = "black", fill = "white", size = 0.5, linetype = "dashed") +
  #geom_text(aes(label = paste0(round(prop, 3) * 100, "%"), y = 0.05), size = 2) +
  geom_text(aes(label = sig, x = 3.5, y = 0.92)) +
  geom_segment(aes(x = 1, xend = 6, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~type, nrow = 1) +
  theme_dakota() +
  ylim(c(0, 1)) +
  guides(fill = F) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    axis.title.x = element_blank()
  ) +
  labs(y = "Proportion") +
  scale_fill_brewer(palette = "Set2")

@@

data_fig4 <- elife %>%
  filter(initial_decision_made) %>%
  gather(author_key, value = gender, ca_gender, la_gender, fa_gender) %>%
  filter(gender %in% c('M', 'F')) %>%
  group_by(author_key) %>%
  mutate(
    # if not ocnsidering the corr. author, then the count is all full submissions, ie: for when a submission ia made
    total_papers = ifelse(author_key == "ca_gender", n(), sum(has_full_submission))
    )%>%
  group_by(author_key, gender) %>%
  summarize(
        paper_count = n(),
        accept_count = sum(accepted == TRUE, na.rm = T),
        encourage_count = sum(encouraged == TRUE),
        encourage_rate = ifelse(author_key[1] == "ca_gender", encourage_count / n(), NA),
        # this accept rate is the number of accepted papers / number of initial + full submissions
        accept_rate = ifelse(author_key[1] == "ca_gender", accept_count / sum(!has_full_submission | full_decision_made, na.rm = T), NA),
        submit_rate = n() / total_papers[1],
        # this is the number of accepted papers divided by all papers 
        encourage_accept_rate = accept_count / sum(has_full_submission & full_decision_made, na.rm = T)
  ) %>%
  ungroup() %>%
  gather(measure_key, value = measurement, encourage_accept_rate) %>%
  left_join(sig_df, by = c("measure_key", "author_key")) %>%
  mutate(
    author_key = factor(author_key,
                        levels = c("ca_gender", "fa_gender", "la_gender"),
                        labels = c("ca_gender" = "Corresponding Author", "fa_gender" = "First Author", "la_gender" = "Last Author")
                        ),
    measure_key = factor(measure_key, 
                         labels = c("submit_rate" = "Submissions", "encourage_rate" = "Enc %", "accept_rate" = "Overall Acc %", "encourage_accept_rate" = "Accept %"),
                         levels = c("submit_rate", "encourage_rate", "accept_rate", "encourage_accept_rate")),
    gender = ifelse(gender == "F", "Female", "Male"),
    standard_error = 1.96 * sqrt( (measurement * (1 - measurement)) / paper_count),
    lower = measurement - standard_error,
    upper = measurement + standard_error
  )

@@

# Firs the first plot, this one will show the proportion that each countrie constitutes the total number of submitted, encouraged, and accepted manuscripts
data_fig5_p1 <- elife %>%
  filter(initial_decision_made & (full_decision_made | full_decision_date_isNA) & !is.na(ca_country)) %>%
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>% # capitalize first letter of country stirngs
  group_by(ca_country) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_count = sum(encouraged == TRUE, na.rm = T),
    full_submissions = sum(has_full_submission),
    prop_of_full =  full_submissions / total_full_submissions,
    prop_of_initial = paper_count / total_submissions,
    prop_of_encouraged = encourage_count / total_encouraged,
    prop_of_accepted = accept_count / total_accepted
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  top_n(8, totals) %>%
  gather(prop_key, value = prop, prop_of_initial, prop_of_full, prop_of_accepted) %>%
  mutate(prop_key = factor(prop_key, 
                           levels = c("prop_of_initial", "prop_of_full", "prop_of_accepted"),
                           labels = c("prop_of_initial" = "Prop. of Initial Submissions", 
                                      "prop_of_full" = "Prop. of Full Submissions", 
                                      "prop_of_accepted" = "Prop. of Accepted Submissions")),
         ca_country = reorder(ca_country, paper_count)
  )

@@

data_fig5_p2 <- elife %>%
  filter(initial_decision_made & (full_decision_made | full_decision_date_isNA) & !is.na(ca_country)) %>%
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>% # capitalize first letter of country stirngs
  group_by(ca_country) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_count = sum(encouraged == TRUE, na.rm = T),
    encourage_rate = encourage_count / paper_count,
    accept_rate = accept_count / sum(!has_full_submission | full_decision_made, na.rm = T),
    encourage_accept_rate = accept_count / sum(has_full_submission & full_decision_made, na.rm = T)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  top_n(8, totals) %>%
  mutate(
    ca_country = reorder(ca_country, encourage_accept_rate)
  ) %>%
  gather(measure_key, value = measurement, encourage_rate, accept_rate, encourage_accept_rate) %>%
  mutate(measure_key = factor(measure_key, 
                           levels = c("encourage_accept_rate", "encourage_rate", "accept_rate"),
                           labels = c("encourage_accept_rate" = "% of full submissions accepted",
                                      "encourage_rate" = "% of initial submissions encouraged", 
                                      "accept_rate" = "% of initial submissions accepted"
                                      ))
  ) %>%
  group_by(measure_key) %>%
  mutate(
    se = 1.96 * sqrt(measurement * (1 - measurement) / paper_count),
    lower = measurement - se,
    upper = measurement + se
  )

@@

fig6 <- grid.arrange(p1, p2)
ggsave("figures/main/fig_6.tiff", plot = fig6, height = 6, width = 8)
ggsave("figures/main/fig_6.png", plot = fig6, height = 6, width = 8)
```

@@

fig7.A <- elife %>%
  filter(full_decision_made & has_full_submission & ca_country %in% countries) %>%
  group_by(ca_country, ca_country_homophily) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_accept_rate = accept_count / paper_count,
    se = 1.96 * sqrt( (encourage_accept_rate * (1 - encourage_accept_rate)) / paper_count),
    lower = encourage_accept_rate - se,
    upper = encourage_accept_rate + se,
    upper = ifelse(upper > 1, 1, upper)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  left_join(sig_df) %>%
  #top_n(16, totals) %>% # 8 countries, 3 authorship types per country, therefore first 24 rows
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>%
  # Start ggplot
  ggplot(aes(x = ca_country_homophily, y = encourage_accept_rate, fill = ca_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 0.1), size = 2.5) +
  geom_text(aes(label = sig, x = 1.5, y = 0.95)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~ca_country, nrow = 2, ncol = 4) +
  ylim(0, 1) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted"
  ) +
  theme(
    axis.text.x = element_text(angle = 20, vjust = 1, hjust = 1)
  )

@@

fig7.B <- d1.summ %>%
  union(d2.summ) %>%
  union(d3.summ) %>%
  left_join(sig_df, by = "type") %>%
  mutate(type = factor(type, 
                       levels = c("all", "no us", "no founder"),
                       labels = c("All Countries", "Excluding U.S.", "Excluding Founding Nations")
                       )
         ) %>%
  ggplot(aes(x = ca_country_homophily, y = encourage_accept_rate, fill = ca_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 0.35), size = 2.5) +
  geom_text(aes(label = sig, x = 1.5, y = 0.65)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.6, 1.1), yend = ifelse(sig != "N/A", 0.6, 1.1)), color = "black") +
  facet_wrap(~type, nrow = 3) +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted"
  )

@@

ggsave("figures/main/fig_7.tiff", plot = fig7, height = 4, width = 7)
ggsave("figures/main/fig_7.png", plot = fig7, height = 4, width = 7)
```

@@

```{r}
fig_SI.1.A <- elife %>%
  filter(full_decision_made & has_full_submission & la_country %in% countries) %>%
  group_by(la_country) %>%
  summarize(
    avg_revisions = mean(num_revisions)
  ) %>%
  ggplot(aes(x = reorder(la_country, -avg_revisions), y = avg_revisions)) +
  geom_bar(stat = "identity", fill = "dodgerblue4", alpha = 0.8, color = "black") +
  theme_dakota() +
  labs(x = "Country of last author",
       y = "Average number of revisions",
       title = "Avg. revisions by country") +
  coord_cartesian(ylim = c(0.5, 0.85)) +
  theme(
    plot.title = element_text(size = 12, margin = margin(0, 0, 2, 0)),
    axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1)
        )

fig_SI.1.B <- elife %>%
  filter(full_decision_made & has_full_submission & la_gender %in% c("M", "F")) %>%
  group_by(la_gender) %>%
  summarize(
    avg_revisions = mean(num_revisions)
  ) %>%
  ggplot(aes(x = la_gender, y = avg_revisions, fill = la_gender)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  theme_dakota() +
  labs(x = "Gender of last author",
       y = "Average number of revisions", 
       title = "Avg. revisions by gender") +
  guides(fill = FALSE) +
  coord_cartesian(ylim = c(0.5, 0.85)) +
  theme(plot.title = element_text(size = 12, margin = margin(0, 0, 2, 0)))

>>>>

---
title: 'Gender and international diversity improves equity in peer review'
author: "Dakota Murray"
output:
  html_document:
    df_print: paged
  html_notebook: default
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
  pdf_document: default
---

@@

> Submissions and selectivity of eLife over time. Left: Yearly count of initial submissions, encouraged initial submissions, and accepted full submissions to eLife between 2012 and 2016; Right: rate of initial submissions encouraged (Encourage %), rate of full submissions accepted (% Full accepted) and rate of initial submissions accepted (Overall accept %) between 2012 and 2016. Submissions during the year of 2017 were excluded because we do not have sufficient data for full life-cycle of these manuscripts.

@@

p1 <- d1 %>%
  ggplot(aes(x = submission_year, y = measurement, linetype = measure_key, color = measure_key, shape = measure_key)) +
  geom_line() +
  geom_point(size = 2) +
  theme_dakota() +
  labs(
    x = "Submission Year",
    y = "# Manuscripts"
  ) +
  scale_color_manual(labels = c("accept_count" = "# Accepted", "encourage_count" = "# Encouraged", "paper_count" = "# Submitted"), values = c("black", "blue", "red")) +
  scale_shape_discrete(labels = c("accept_count" = "# Accepted", "encourage_count" = "# Encouraged", "paper_count" = "# Submitted")) +
  scale_linetype_discrete(labels = c("accept_count" = "# Accepted", "encourage_count" = "# Encouraged", "paper_count" = "# Submitted"))

d2 <- elife %>%
  group_by(submission_year) %>%
  summarize(
        paper_count = n(),
        accept_count = sum(accepted == TRUE, na.rm = T),
        encourage_count = sum(encouraged == TRUE, na.rm = T),
        encourage_rate = encourage_count / paper_count,
        accept_rate = accept_count / paper_count,
        encourage_accept_rate = accept_count / sum(!is.na(full_decision_made) & full_decision_made)
  ) %>%
  gather(measure_key, value = measurement, encourage_rate, accept_rate, encourage_accept_rate) %>%
  mutate(
    measure_key = factor(measure_key, levels = c("encourage_rate", "encourage_accept_rate", "accept_rate"))
  ) %>%
  filter(submission_year < 2017)

p2 <- d2 %>%
  ggplot(aes(x = submission_year, y = measurement, linetype = measure_key, color = measure_key, shape = measure_key)) +
  geom_line() +
  geom_point(size = 2) +
  ylim(0, 1) +
  theme_dakota() +
  labs(
    x = "Submission Year",
    y = "%"
  ) +
  scale_color_manual(labels = c("accept_rate" = "Overall accept %", "encourage_rate" = "Encourage %", "encourage_accept_rate" = "% Full accepted"), 
                     values = c("blue", "purple", "red")) +
  scale_shape_manual(labels = c("accept_rate" = "Overall accept %", "encourage_rate" = "Encourage %", "encourage_accept_rate" = "% Full accepted"),
                     values = c(17, 15, 18)) +
  scale_linetype_manual(labels = c("accept_rate" = "Overall accept %", "encourage_rate" = "Encourage %", "encourage_accept_rate" = "% Full accepted"), 
                          values = c("dotted", "dashed", "dotdash"))

fig2 <- grid.arrange(p1, p2, ncol = 2)
ggsave("figures/main/fig_2.tiff", plot = fig2, height = 4, width = 7.5)
ggsave("figures/main/fig_2.png", plot = fig2, height = 4, width = 7.5)

@@

p1 <- people %>%
  filter(gender %in% c("M", "F")) %>%
  mutate(gender = ifelse(gender == "M", "Male", "Female")) %>%
  group_by(type) %>%
  mutate(total = n()) %>%
  group_by(type, gender) %>%
  summarize(
    prop = n() / total[1]
  ) %>%
  ungroup() %>%
  left_join(expected, by = "gender") %>%
  left_join(sig_df, by = c("gender", "type")) %>%
  mutate(
    type = factor(type, 
                  levels = c("Gatekeeper", "Corr. Author", "First Author", "Last Author"),
                  labels = c("Gatekeeper" = "Gatekeeper", "Corr. Author" = "Corresponding", "First Author" = "First", "Last Author" = "Last")),
    sig = as.character(sig)
  ) %>%
  # start ggplot
  ggplot(aes(x = gender, y = prop, fill = gender)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_bar(stat = "identity", aes(y = expected_prop), alpha = 0, color = "black", fill = "white", size = 0.5, linetype = "dashed") +
  #geom_text(aes(label = paste0(round(prop, 3) * 100, "%"), y = 0.1), size = 3) +
  geom_text(aes(label = ifelse(sig == "N/A", "", sig), x = 1.5, y = 0.9)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~type, nrow = 1) +
  theme_dakota() +
  ylim(c(0, 1)) +
  theme(
    axis.title.x = element_blank(),
    legend.position = "right"
  ) +
  labs(y = "Proportion") +
  guides(fill = F)

@@

p2 <- people %>%
  group_by(type) %>%
  mutate(total = n()) %>%
  filter(continent != "Antarctica") %>%
  group_by(type, continent) %>%
  summarize(
    prop = n() / total[1]
  ) %>%
  ungroup() %>%
  left_join(expected, by = "continent") %>%
  left_join(sig_df, by = c("continent", "type")) %>%
  mutate(
    type = factor(type, 
                  levels = c("Gatekeeper", "Corr. Author", "First Author", "Last Author"),
                  labels = c("Gatekeeper" = "Gatekeeper", "Corr. Author" = "Corresponding", "First Author" = "First", "Last Author" = "Last")),
    continent = reorder(continent, -prop),
    sig = as.character(sig)
  ) %>%
  # start ggplot
  ggplot(aes(x = continent, y = prop, fill = continent)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_bar(stat = "identity", aes(y = expected_prop), alpha = 0, color = "black", fill = "white", size = 0.5, linetype = "dashed") +
  #geom_text(aes(label = paste0(round(prop, 3) * 100, "%"), y = 0.05), size = 2) +
  geom_text(aes(label = ifelse(sig == "N/A", "", sig), x = 3.5, y = 0.92)) +
  geom_segment(aes(x = 1, xend = 6, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~type, nrow = 1) +
  theme_dakota() +
  ylim(c(0, 1)) +
  guides(fill = F) +
  theme(
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    axis.title.x = element_blank()
  ) +
  labs(y = "Proportion") +
  scale_fill_brewer(palette = "Set2")

@@

data_fig4 <- elife %>%
  filter(initial_decision_made) %>%
  gather(author_key, value = gender, ca_gender, la_gender, fa_gender) %>%
  filter(gender %in% c('M', 'F')) %>%
  group_by(author_key) %>%
  mutate(
    # if not ocnsidering the corr. author, then the count is all full submissions, ie: for when a submission ia made
    total_papers = ifelse(author_key == "ca_gender", n(), sum(has_full_submission))
    )%>%
  group_by(author_key, gender) %>%
  summarize(
        paper_count = n(),
        accept_count = sum(accepted == TRUE, na.rm = T),
        encourage_count = sum(encouraged == TRUE),
        encourage_rate = ifelse(author_key[1] == "ca_gender", encourage_count / n(), NA),
        # this accept rate is the number of accepted papers / number of initial + full submissions
        accept_rate = ifelse(author_key[1] == "ca_gender", accept_count / sum(!has_full_submission | full_decision_made, na.rm = T), NA),
        submit_rate = n() / total_papers[1],
        # this is the number of accepted papers divided by all papers 
        encourage_accept_rate = accept_count / sum(has_full_submission & full_decision_made, na.rm = T)
  ) %>%
  ungroup() %>%
  gather(measure_key, value = measurement, encourage_accept_rate) %>%
  left_join(sig_df, by = c("measure_key", "author_key")) %>%
  mutate(
    author_key = factor(author_key,
                        levels = c("ca_gender", "fa_gender", "la_gender"),
                        labels = c("ca_gender" = "Corresponding", "fa_gender" = "First", "la_gender" = "Last")
                        ),
    measure_key = factor(measure_key, 
                         labels = c("submit_rate" = "Submissions", "encourage_rate" = "Enc %", "accept_rate" = "Overall Acc %", "encourage_accept_rate" = "Accept %"),
                         levels = c("submit_rate", "encourage_rate", "accept_rate", "encourage_accept_rate")),
    gender = ifelse(gender == "F", "Female", "Male"),
    standard_error = 1.96 * sqrt( (measurement * (1 - measurement)) / paper_count),
    lower = measurement - standard_error,
    upper = measurement + standard_error
  )

@@

# Firs the first plot, this one will show the proportion that each countrie constitutes the total number of submitted, encouraged, and accepted manuscripts
data_fig5_p1 <- elife %>%
  filter(initial_decision_made & (full_decision_made | full_decision_date_isNA) & !is.na(ca_country)) %>%
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>% # capitalize first letter of country stirngs
  group_by(ca_country) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_count = sum(encouraged == TRUE, na.rm = T),
    full_submissions = sum(has_full_submission),
    prop_of_full =  full_submissions / total_full_submissions,
    prop_of_initial = paper_count / total_submissions,
    prop_of_encouraged = encourage_count / total_encouraged,
    prop_of_accepted = accept_count / total_accepted
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  top_n(8, totals) %>%
  gather(prop_key, value = prop, prop_of_initial, prop_of_full, prop_of_accepted) %>%
  mutate(prop_key = factor(prop_key, 
                           levels = c("prop_of_initial", "prop_of_full", "prop_of_accepted"),
                           labels = c("prop_of_initial" = "Prop. of initial submissions", 
                                      "prop_of_full" = "Prop. of full submissions", 
                                      "prop_of_accepted" = "Prop. of accepted submissions")),
         ca_country = reorder(ca_country, paper_count)
  )

@@

data_fig5_p2 <- elife %>%
  filter(initial_decision_made & (full_decision_made | full_decision_date_isNA) & !is.na(ca_country)) %>%
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>% # capitalize first letter of country stirngs
  group_by(ca_country) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_count = sum(encouraged == TRUE, na.rm = T),
    encourage_rate = encourage_count / paper_count,
    accept_rate = accept_count / sum(!has_full_submission | full_decision_made, na.rm = T),
    encourage_accept_rate = accept_count / sum(has_full_submission & full_decision_made, na.rm = T)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  top_n(8, totals) %>%
  mutate(
    ca_country = reorder(ca_country, encourage_rate)
  ) %>%
  gather(measure_key, value = measurement, encourage_rate, accept_rate, encourage_accept_rate) %>%
  mutate(measure_key = factor(measure_key, 
                           levels = c("encourage_rate", "encourage_accept_rate", "accept_rate"),
                           labels = c("encourage_rate" = "% of initial submissions encouraged", 
                                      "encourage_accept_rate" = "% of full submissions accepted",
                                      "accept_rate" = "% of initial submissions accepted"
                                      ))
  ) %>%
  group_by(measure_key) %>%
  mutate(
    se = 1.96 * sqrt(measurement * (1 - measurement) / paper_count),
    lower = measurement - se,
    upper = measurement + se
  )

@@

fig6 <- grid.arrange(p1, p2)
ggsave("figures/main/fig_6.tiff", plot = fig6, height = 6, width = 7.5)
ggsave("figures/main/fig_6.png", plot = fig6, height = 6, width = 7.5)
```

@@

fig7.A <- elife %>%
  filter(full_decision_made & has_full_submission & ca_country %in% countries) %>%
  group_by(ca_country, ca_country_homophily) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_accept_rate = accept_count / paper_count,
    se = 1.96 * sqrt( (encourage_accept_rate * (1 - encourage_accept_rate)) / paper_count),
    lower = encourage_accept_rate - se,
    upper = encourage_accept_rate + se,
    upper = ifelse(upper > 1, 1, upper)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  left_join(sig_df) %>%
  #top_n(16, totals) %>% # 8 countries, 3 authorship types per country, therefore first 24 rows
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>%
  # Start ggplot
  ggplot(aes(x = ca_country_homophily, y = encourage_accept_rate, fill = ca_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 0.075), size = 2.5) +
  geom_text(aes(label = sig, x = 1.5, y = 0.95)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~ca_country, nrow = 2, ncol = 4) +
  ylim(0, 1) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted"
  ) +
  theme(
    axis.text.x = element_text(angle = 20, vjust = 1, hjust = 1)
  )

@@

fig7.B <- d1.summ %>%
  union(d2.summ) %>%
  union(d3.summ) %>%
  left_join(sig_df, by = "type") %>%
  mutate(type = factor(type, 
                       levels = c("all", "no us", "no founder"),
                       labels = c("All Countries", "Excluding U.S.", "Excluding Founding Nations")
                       )
         ) %>%
  ggplot(aes(x = ca_country_homophily, y = encourage_accept_rate, fill = ca_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 0.32), size = 2.5) +
  geom_text(aes(label = sig, x = 1.5, y = 0.65)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.6, 1.1), yend = ifelse(sig != "N/A", 0.6, 1.1)), color = "black") +
  facet_wrap(~type, nrow = 3) +
  coord_cartesian(ylim = c(0.3, 0.7)) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted"
  )

@@

ggsave("figures/main/fig_7.tiff", plot = fig7, height = 5, width = 7.5)
ggsave("figures/main/fig_7.png", plot = fig7, height = 5, width = 7.5)
```

@@

```{r}
fig_SI.1.A <- elife %>%
  filter(full_decision_made & has_full_submission & la_country %in% countries) %>%
  group_by(la_country) %>%
  summarize(
    avg_revisions = mean(num_revisions)
  ) %>%
  mutate(la_country = factor(sapply(as.character(la_country), simpleCap))) %>% # capitalize first letter of country stirngs
  ggplot(aes(x = reorder(la_country, -avg_revisions), y = avg_revisions)) +
  geom_bar(stat = "identity", fill = "dodgerblue4", alpha = 0.8, color = "black") +
  theme_dakota() +
  labs(x = "Country of last author",
       y = "Average number of revisions",
       title = "Avg. revisions by country") +
  coord_cartesian(ylim = c(0.5, 0.85)) +
  theme(
    plot.title = element_text(size = 12, margin = margin(0, 0, 2, 0)),
    axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1)
        )

fig_SI.1.B <- elife %>%
  filter(full_decision_made & has_full_submission & la_gender %in% c("M", "F")) %>%
  group_by(la_gender) %>%
  summarize(
    avg_revisions = mean(num_revisions)
  ) %>%
  mutate(
    la_gender = ifelse(la_gender == "M", "Male", "Female")
  ) %>%
  ggplot(aes(x = la_gender, y = avg_revisions, fill = la_gender)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  theme_dakota() +
  labs(x = "Gender of last author",
       #y = "Average number of revisions", 
       y = "",
       title = "Avg. revisions by gender") +
  guides(fill = FALSE) +
  coord_cartesian(ylim = c(0.5, 0.85)) +
  theme(plot.title = element_text(size = 12, margin = margin(0, 0, 2, 0)))
